Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-21 paper_comparison/appendix.Rmd
update text for alpha

The parameter $\alpha$ used for the $p$-value calculation needs to be estimated from responses to null lineups. However, The way we generate Rorschach lineup is not strictly the same as what suggested in @vanderplas2021statistical and @buja_statistical_2009. Therefore, we conduct a sensitivity analysis in this section to examine the impact of the variation of the estimator $\alpha$ on our primary findings.

The analysis is conducted by setting up several scenarios, where the $\alpha$ is under or overestimated by 12.5%, 25%, 50% and 100%. Using the adjusted $\hat{\alpha}$, we recalculate the $p$-value for every lineup and show the results in Figure \ref{fig:sensitive}. It can be observed that there are some changes to $p$-values, especially when the $\hat{\alpha}$ is deflated. However, Figure \ref{fig:sensitive-barplot} shows that adjusting $\hat{\alpha}$ will not result in a huge difference in rejection decisions. There are only a small number of cases (12 out of 558) where the rejection decision changes. It is very unlikely the downstream findings will be affected because of the estimate of $\alpha$.

@@

```{r}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  group_by(modified) %>%
  count(adjusted_reject = adjusted_p_value <= 0.05, reject = p_value <= 0.05) %>%
  complete(adjusted_reject, reject, fill = list(n = 0)) %>%
  ungroup() %>%
  filter(adjusted_reject != reject) %>%
  mutate(case = ifelse(!adjusted_reject, "p-value < 0.05 but adjusted p-value > 0.05", "p-value > 0.05 but adjusted p-value < 0.05")) %>%
  rename(multiplier = modified) %>%
  select(-adjusted_reject, -reject) %>%
  pivot_wider(names_from = case, values_from = n) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "sensitivity", 
                    escape = FALSE,
                    caption = "Change of rejection decision because of the modification of $\\alpha$.")
```

>>>>

The parameter $\alpha$ used for the $p$-value calculation needs to be estimated from responses to null lineups. With a greater value of $\hat{\alpha}$, the $p$-value will be smaller, resulting in more lineups being rejected. However, The way we generate Rorschach lineup is not strictly the same as what suggested in @vanderplas2021statistical and @buja_statistical_2009. Therefore, we conduct a sensitivity analysis in this section to examine the impact of the variation of the estimator $\alpha$ on our primary findings.

The analysis is conducted by setting up several scenarios, where the $\alpha$ is under or overestimated by 12.5%, 25% and 50%. Using the adjusted $\hat{\alpha}$, we recalculate the $p$-value for every lineup and show the results in Figure \ref{fig:sensitive}. It can be observed that there are some changes to $p$-values, especially when the $\hat{\alpha}$ is multiplied by 50%. However, Table \ref{tab:sensitive} shows that adjusting $\hat{\alpha}$ will not result in a huge difference in rejection decisions. There are only a small number of cases where the rejection decision change, considering there are a total of 279 lineups with uniform fitted value distribution. It is very unlikely the downstream findings will be affected because of the estimate of $\alpha$.

@@

```{r}
upper_lower_p %>%
  left_join(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform") %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value = first(p_value))) %>%
  group_by(modified) %>%
  count(adjusted_reject = adjusted_p_value <= 0.05, reject = p_value <= 0.05) %>%
  complete(adjusted_reject, reject, fill = list(n = 0)) %>%
  ungroup() %>%
  filter(adjusted_reject != reject) %>%
  mutate(case = ifelse(!adjusted_reject, "p-value < 0.05 but adjusted p-value > 0.05", "p-value > 0.05 but adjusted p-value < 0.05")) %>%
  rename(multiplier = modified) %>%
  select(-adjusted_reject, -reject) %>%
  pivot_wider(names_from = case, values_from = n) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE, label = "sensitivity", 
                    escape = FALSE,
                    caption = "Change of rejection decision because of the modification of $\\hat{\\alpha}$.")
```
